A dispatch-based approach to fully allocate costs in optimal power systems

### 2020-09-08 paper/flow_based.tex
follow up

\begin{figure*}
    \includegraphics[width=\linewidth]{de50bf/capex_duration_curve}
    \caption{Duration curve of the CAPEX allocation for production and storage technologies. Hours are sorted such that the total amount of allocated expenditure per hour decreases. With 2.7 bn~\euro\, the first value pushes investments extraordinary high. It is dominated by CAPEX for OCGT to which 92\% of the payments are allocated. This hour alone occasions about half of all OCGT CAPEX. The remaining time-steps are dominated by revenues for onshore wind.}
    \label{fig:capex_duration}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{de50bf/capex_duration_curve}
    \caption{Duration curve of the CAPEX allocation for production and storage technologies. Hours are sorted such that the total amount of allocated expenditure per hour decreases. With 2.7 bn~\euro\, the first value pushes investments extraordinary high. It is dominated by CAPEX for OCGT to which 92\% of the payments are allocated. This hour alone occasions about the half of all OCGT CAPEX. The following 7000 time-steps are dominated by revenues for onshore wind and reveal a rather even distribution. In hours of low CAPEX allocation (after the second drop) spendings for OCGT start to increase again. These  }
    \label{fig:capex_duration}
\end{figure*}
